Shallow EDSLs and Object-Oriented Programming

### 2018-12-17 Programming19/Main.tex
Addressing problems
Table

% Bibliography
%\renewcommand{\section}[1]{\oldsec{#1}}

>>>>

% Bibliography
%\renewcommand{\section}[1]{\oldsec{#1}}
\acks We thank Willam R. Cook, Jeremy Gibbons, Ralf Hinze, Martin Erwig, and the
anonymous reviewers of GPCE, ICFP, JFP, and Programming for their valuable
comments that significantly improved this work. This work is based on the first
author's master thesis~\cite{zhang2017extensible} and has been funded by Hong
Kong Research Grant Council projects number 17210617 and 17258816.
